---
title: "Reproducible Research: Peer Assessment 1 - Alex Fleming"
output: 
  html_document:
    keep_md: true
---
This assignment makes use of data from a personal activity monitoring device. This device collects data at 5 minute intervals through out the day. The data consists of two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day.

**steps**: Number of steps taking in a 5-minute interval (missing values are coded as `NA`)
**date**: The date on which the measurement was taken in YYYY-MM-DD format
**interval**: Identifier for the 5-minute interval in which measurement was taken

## Loading and preprocessing the data
```{r loading, echo=TRUE}
library(data.table)
data <- fread(unzip("activity.zip"))



```

## What is mean total number of steps taken per day?
```{r means, echo=TRUE}


```
## What is the average daily activity pattern?
```{r pattern, echo=TRUE}


```
## Imputing missing values
```{r missing, echo=TRUE}


```
## Are there differences in activity patterns between weekdays and weekends?
```{r weekday, echo=TRUE}

```

# Closeout Comments - 
